A sustainable approach to tourist signage on heritage trails\footnote{This research has been supported by the Ministry of University and Research under the "Underlandscape" project (2020428LS8)}

### 2023-11-08 paper.tex
Post call 8/11

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad University of Pisa (retired); augusto.ciuffoletti@unipi.it\\
$^{2}$ \quad University of Pisa; mariagrazia.deri@sp.unipi.it\\
$^{3}$ \quad University of Pisa; l.chiti2@studenti.unipi.it}

@@

Section \ref{sec:methods} provides the multidisciplinary framework. Section \ref{sec:legacy} illustrates the legacy emphasizing historical facts and locations. Section \ref{sec:tourism} describes the social and touristic context of the target location and provides the guidelines for integrating the initiative in the socio-political fabric. Such guidelines are used to define an agenda, in section \ref{sec:agenda}, and the section is concluded by a reasoned description of the area, highlighting the points of interest and their reachability \ref{sec:soa}.

@@

The way to improve the valorization and enjoyment of this area applies to a slow tourism approach. This approach can involve the community, especially in the southern part of the municipality, which is still less frequented, more hilly, and therefore less traveled by the network of trails. We envision the creation of geo-itineraries characterized by the rediscovery of the historical roads, partly well-preserved, which connected the villages with the valley bottom and between them, including those sites of interest that encapsulate the history of this area, starting with the caves.

@@

\begin{table}
    \footnotesize
    \setstretch{1,2}
    \centering
    \begin{tabular}{l||l|l} \hline 
        {\bf Region} & {\bf Bagni di Lucca} & {\bf Lucca} \\ \hline
        Resident density (residents/{$km^2$}) & 33.95 & 215.71 \\
        Touristic density (visitors/{$km^2$}) & 106.41 & 1866.96 \\
        Average stay  (days) &  2.98 &  3.36 \\
        Accommodation density (accommodations/{$km^2$}) & 10.14 & 19.30 \\
        Coexistence (100 $\times$ Foreign/Italian) & 103.74\% &  69.87\% \\ 
         \hline
    \end{tabular}
    \caption{Tourist indexes in \emph{Bagni di Lucca}
%. The {\em touristic density} is the number of tourists in a year per $km^2$. The {\em average stay} is the average number of nights spent in town by tourists. The {\em accommodation density} is the rate between the number of touristic presences and the number of beds occupied by tourists in a year. The {\em Coexistence} is the percent rate between foreign and Italian tourists.
}
    \label{tab:tourism}
\end{table}

@@

\subsubsection{Our activity \label{sec:agenda}}

@@

\subsubsection{Sites and trail’s state of art \ref{sec:soa}}

@@

A different application-based solution privileging passive devices is based on a writable NFC tag close to the one delivering the content. To update the number of visitors that have read the informational NFC, the user application reads and increments the count recorded on the writable NFC. Here too the primary drawback compared with our QR-tag based solution is the need for an ad-hoc application. In addition, the event of data pollution is not excluded.

>>>>

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad University of Pisa (retired); augusto.ciuffoletti@unipi.it\\
$^{2}$ \quad University of Pisa; mariagrazia.deri@sp.unipi.it\\
$^{3}$ \quad University of Pisa; letizia.chiti@}

@@

Section \ref{sec:methods} provides the multidisciplinary framework. Section \ref{sec:legacy} illustrates the legacy emphasizing historical facts and locations. Section \ref{sec:tourism} describes the social and touristic context of the target location and provides the guidelines for integrating the initiative in the socio-political fabric. Such guidelines are used to motivate and define an agenda, in section \ref{sec:agenda}, and the section is concluded by a reasoned description of the area, highlighting the points of interest and their reachability \ref{sec:soa}.

@@

The way to improve the valorization and enjoyment of this area applies to a slow tourism approach. This approach can involve the community, especially in the southern part of the municipality, which is still less frequented, more hilly, and therefore less traveled by the network of trails. We envision the creation of heritage trails characterized by the rediscovery of the historical roads, partly well-preserved, which connected the villages with the valley bottom and between them, including those sites of interest that encapsulate the history of this area, starting with the caves.

@@

\begin{table}
    \footnotesize
    \setstretch{1,2}
    \centering
    \begin{tabular}{l||l|l} \hline 
        {\bf Region} & {\bf Bagni di Lucca} & {\bf Lucca} \\ \hline
        Resident density (residents/{$km^2$}) & 33.95 & 215.71 \\
        Touristic density (visitors/{$km^2$}) & 106.41 & 1866.96 \\
        Average stay  (days) &  2.98 &  3.36 \\
        Accommodation density (accommodations/{$km^2$}) & 10.14 & 19.30 \\
        Coexistence (100 $\times$ Foreign/Italian) & 103.74\% &  69.87\% \\ 
         \hline
    \end{tabular}
    \caption{Tourist indexes in \emph{Bagni di Lucca} in 2022
%. The {\em touristic density} is the number of tourists in a year per $km^2$. The {\em average stay} is the average number of nights spent in town by tourists. The {\em accommodation density} is the rate between the number of touristic presences and the number of beds occupied by tourists in a year. The {\em Coexistence} is the percent rate between foreign and Italian tourists.
}
    \label{tab:tourism}
\end{table}

@@

\subsubsection{How top implement the guidelines? \label{sec:agenda}}

@@

\subsubsection{Sites and trail’s state of the art \ref{sec:soa}}

@@
